\documentclass[10pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Coursera Capstone Proposal - Suicide Rates}
\author{Manuel Ramsaier \\
	RWU University, Germany \\
}

\date{\today}
% Hint: \title{what ever}, \author{who care} and \date{when ever} could stand 
% before or after the \begin{document} command 
% BUT the \maketitle command MUST come AFTER the \begin{document} command! 
\begin{document}
	
	\maketitle
	
	
	\begin{abstract}
		Later there will be an abstract here
	\end{abstract}
	
	\section{Introduction}
	Suicide is a sad way of ending a life that could have been full of joy and love. It is of great interest to me to find out what drives a person to kill himself and I found a good data source for a lot of suicides over the last decades. 
	
	\section{Problem Statement}

	First, I will just look into the data set and filter it by its columns. For example, do more men or women commit suicide? How many woman from Germany which are seen as coming from the Generation X and why so many or why so few. \\
	
	The approach, I want to take with this data is different to the ones taken before on this data set. I want to predict a living person's probability to have committed suicide in the past, based on a user input for the data. \\

	
	\section{Approach}
	
	 I am right now not entirely sure which algorithm I want to use for this. As the data set is large, I will reduce it to one country only (as the user later is asked to input, where he or she comes from) . Based on this data set, I will explore it a bit with different clustering and regression techniques.
	 
	 
	 
	\section{Data used} \label{documentclasses}
	
	The suicide data is taken from kaggle \href{https://www.kaggle.com/russellyates88/suicide-rates-overview-1985-to-2016}{\nolinkurl{here}}. 
	

%	\begin{itemize}
%		\item article
%		\item book 
%		\item report 
%		\item letter 
%	\end{itemize}
	
	
%	\begin{enumerate}
%		\item article
%		\item book 
%		\item report 
%		\item letter 
%	\end{enumerate}
%	
%	\begin{description}
%		\item[article\label{article}]{Article is \ldots}
%		\item[book\label{book}]{The book class \ldots}
%		\item[report\label{report}]{Report gives you \ldots}
%		\item[letter\label{letter}]{If you want to write a letter.}
%	\end{description}
%	
%	
%	\section{Conclusions}\label{conclusions}
%	There is no longer \LaTeX{} example which was written by \cite{doe}.
%	
%	
%	\begin{thebibliography}{9}
%		\bibitem[Doe]{doe} \emph{First and last \LaTeX{} example.},
%		John Doe 50 B.C. 
%	\end{thebibliography}
	
\end{document}